---
title: "Visualizing logistic regression"
output:
  html_document:
    css: ~/GitHub/ialsa-2016-groningen/libs/css/sidebar.css
    highlight: kate
    keep_md: yes
    theme: flatly
    toc: yes
---

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 9, 
  fig.width = 13, 
  out.width = "700px",
  fig.path = 'smoke_now-coloring-book/',     
  dev = "png",
  dpi = 400
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./models/poor_health/smoke_now-points-coloring-book.R") 
```

This report explores possible visualization solution for logistic regression modeling.  


<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echoChunks, message=FALSE}
```


<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```


<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put code in here.  It doesn't call a chunk in the codebehind file.
```
# (I) Exposition

> This report is a record of interaction with a data transfer object (dto) produced by `./manipulation/0-ellis-island.R`. 

The next section recaps this script, exposes the architecture of the DTO, and demonstrates the language of interacting with it.   

## (I.A) Ellis Island

> All data land on Ellis Island.

The script `0-ellis-island.R` is the first script in the analytic workflow. It accomplished the following: 

- (1) Reads in raw data files from the candidate studies   
- (2) Extract, combines, and exports their metadata (specifically, variable names and labels, if provided) into `./data/shared/derived/meta-data-live.csv`, which is updated every time Ellis Island script is executed.   
- (3) Augments raw metadata with instructions for renaming and classifying variables. The instructions are provided as manually entered values in `./data/shared/meta-data-map.csv`. They are used by automatic scripts in later harmonization and analysis.  
- (4) Combines unit and metadata into a single DTO to serve as a starting point to all subsequent analyses.   

<!-- Load the datasets.   -->
```{r load-data, echo=T, results='asis', message=FALSE}
```

<!-- Inspect the datasets.   -->
```{r inspect-data, echo=T, results='show', message=FALSE}
```


###  Meta
```{r meta-table, echo=TRUE, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Basic table view.   -->
```{r basic-table, echo=TRUE, results='show', message=FALSE}
```

# (II) Development

## (II.A) Pre-Assembly

### Combined data

```{r combine-from-dto, echo=TRUE, results='show', message=FALSE}
```


```{r assemble, echo=TRUE, results='show', message=FALSE}
```

### Fit
```{r fit-model, echo=TRUE}
```

## Graphs

### Global prob
```{r 1-global-probability, echo=echoChunks}
```

### Global odds
```{r 3-global-odds, echo=echoChunks}
```

### Local prob
```{r 2-local-probability, echo=echoChunks}
```

### Global odds
```{r 4-local-odds, echo=echoChunks}
```








