---
title: "Graphing Phase Only"
date: "Date: `r Sys.Date()`"
output: 
  html_document: 
    keep_md: yes
    toc: yes
    toc_float: yes
    output:
    highlight: tango
    theme: spacelab
---
This report provides demonstration of visualizing the model estimated by 
`./reports/technique-demonstration/technique-demonstration.R`
It does not require access to the raw data, instead it loads only estimated model results. 


<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F} 
# cat("Working directory: ", getwd())
library(knitr)
opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set-options, echo=F}
# cat("Working directory: ", getwd())
report_render_start_time <- Sys.time()
opts_chunk$set(
  results      = 'show', 
  comment      = NA, 
  tidy         = FALSE,
  # dpi        = 400,
  out.width  = "900px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.
  fig.width    = 12, 
  fig.height   = 6, 
  fig.path     = 'figure-png/'
)

echo_chunks    <- TRUE #Toggle for debugging.
message_chunks <- FALSE #Toggle for debugging.
options(width=100) #So the output is 25% wider than the default.
read_chunk("./reports/graphing-phase-only/graphing-phase-only.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

# load sources
<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echo_chunks, message=message_chunks}
```
# load packages
<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echo_chunks, message=message_chunks}
```

# declare globals
<!-- Load any global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echo_chunks, results='show', message=message_chunks}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r rmd-specific, echo=echo_chunks, message=message_chunks}
# Put presentation-specific code in here.  It doesn't call a chunk in the codebehind file.
#   It should be rare (and used cautiously), but sometimes it makes sense to include code in Rmd 
#   that doesn't live in the codebehind R file.
```
# load data
<!-- Load the datasets.   -->
```{r load-data, echo=echo_chunks, results='show', message=message_chunks}
```
# tweek data
<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echo_chunks, results='show', message=message_chunks}
```
# inspect data
```{r inspect-data, echo=echo_chunks, results='show', message=message_chunks}
```
# custom functions
```{r define-utility-functions, echo=echo_chunks, results='show', message=message_chunks}
```

# Graph controls
```{r define-graph-controls, echo=echo_chunks, results='show', message=message_chunks}
```

# Coloring Book setting
```{r define-coloring-book-setting, echo=echo_chunks, results='show', message=message_chunks}
```

# Display 0
```{r print-display-0, echo=echo_chunks, results='show', message=message_chunks}
```

# Display 1
```{r print-display-1, echo=echo_chunks, results='show', message=message_chunks}
```

# Display 2
```{r print-display-2, echo=echo_chunks, results='show', message=message_chunks}
```

# Display 3
```{r print-display-3, echo=echo_chunks, results='show', message=message_chunks}
```

# Display 4
```{r print-display-4, echo=echo_chunks, results='show', message=message_chunks}
```

# Display 5
```{r print-display-5, echo=echo_chunks, results='show', message=message_chunks}
```

# Display 6
```{r print-display-6, echo=echo_chunks, results='show', message=message_chunks}
```

# save to disk
```{r save-to-disk, echo=echo_chunks, results='show', message=message_chunks}
```



# Session Information
For the sake of documentation and reproducibility, the current report was rendered on a system using the following software.
```{r session-info, echo=FALSE}
report_render_duration_in_seconds <- round(as.numeric(difftime(Sys.time(), report_render_start_time, units="secs")))
cat("Report rendered by", Sys.info()["user"], "at", strftime(Sys.time(), "%Y-%m-%d, %H:%M %z"), "in", report_render_duration_in_seconds, "seconds." )
sessionInfo()
```
